BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-07-15 Paper/BOAST.tex
improved BOAST description

  \begin{itemize}
  \item Abstraction of programming concepts: variables, procedures
  \item Operator overloading: simpler syntax
  \item Two languages in one
  \end{itemize}

@@

   multitarget generation
   compilation
   execution
  + dumper et replay pour tests de non régression

>>>>

  \begin{itemize}
  \item Abstraction of programming concepts: variables, procedures (
portability, productivity )
  \item Operator overloading: simpler syntax ( productivity, portability )
  \item Two languages in one ( productivity, performance ) 
  \end{itemize}

@@

   multi target language generation ( performance, portability )
   compilation ( productivity, performance )
   execution ( productivity, performance )
  + dumper et replay pour tests de non régression ( productivity )
